### 2015-02-15 fundamentals/impl.tex

Trades are initiated by the \Cyclus kernel after a solution to the \gls{DRE} is
found. The \gls{DRE} is executed at each time step. Therefore, if a facility's
request for a resource is not met at a given time step, it may offer a request
in the proceeding time step.

>>>>

Trades between agents are initiated by the \Cyclus kernel after a solution to
the \gls{DRE} is found. For each trade, the supplying agent is notified of its
matched request and provides an associated resource to the exchange. All
supplied resources are then sent to the corresponding requesting agents.

In \Cyclus, the \gls{DRE} is executed at each time step. Therefore, if a
facility's request for a resource is not met at a given time step, it may offer
a request in the proceeding time step. Because agent behavior may change
arbitrarily, the exchange executed at any given time step may be unique in a
simulation.

The \gls{DRE} is a novel simulation concept in the nuclear fuel cycle domain. It
provides a flexible supply-demand infrastructure, supporting dynamic flows of
resources between agents. Trading between agents can be affected by both the
proposed quality of a resource and agent relationships through the use of
cardinal preferences. Accordingly, a wide range of possible effects can be
modeled, from capacitated fuel supply to international trade agreements.
